On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-16 paper.tex
conclusions

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling without TabMalloc), for the NS and FS designs, when running
1, 8, 16, 24 and 32 threads, with TabMalloc and, local scheduling
(column \emph{Local}) and batched scheduling (column \emph{Batched})
strategies. In order to give a fair weight to each benchmark, the
overhead ratio is calculated as follows. We begin by running ten times
each benchmark $B$ for each design $D$ with $T$ threads. Then, we
calculate the average of those ten runs and use that value ($D_{BT}$)
to put it in perspective against the base time, which is the average
of the ten runs of the NS design with $1$ thread ($NS_{B1}$). For
that, we use the following formula for the overhead $O_{DBT} = D_{BT}
/ NS_{B1}$.  After calculating all the overheads $O_{DBT}$ for a
certain design $D$ and number of threads $T$ corresponding to the
several benchmarks $B$, we calculate the respective minimum, average,
maximum and standard deviation overhead ratios. Thus, the lowest ratio
is the one that represents lowest overhead and it is the best ratio.

@@

By observing Table~\ref{tab_batched_overhead}, we can see that, for
one thread, on average, local scheduling is sightly better than
batched on the two designs. For the NS design we have $0.78$ and
$0.82$ and for the FS design we have $1.30$ and $1.46$ average
overhead ratios, for the local and batched scheduling strategies,
respectively. As we scale the number of threads, one can observe that,
for the NS design both scheduling strategies have similar minimum,
average and maximum overhead ratios. For the FS design, the best
minimum overhead ratio on $1$, $8$, $16$, $24$ and $32$ threads is
always the batched scheduling. For the average and maximum overhead
ratio, local scheduling is always better than batched
scheduling. However, for the average ratio, the results between both
strategies is quite close. We consider this to be quite significant,
once the FS design with batched scheduling requires the support of the
PAC procedure. For the maximum overhead ratio, the difference between
both strategies is higher than for the average overhead ratio, however
we hope to reduce the difference with further improvements in the PAC
procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Further Work}
.........

>>>>

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling without TabMalloc), for the NS and FS designs, when running
1, 8, 16, 24 and 32 threads, with TabMalloc and, local scheduling
(column \emph{Local}) and batched scheduling (column \emph{Batched})
strategies. In order to give a fair weight to each benchmark, the
overhead ratio is calculated as follows. We begin by running ten times
each benchmark $B$ for each design $D$ with $T$ threads. Then, we
calculate the average of those ten runs and use that value ($D_{BT}$)
to put it in perspective against the base time, which is the average
of the ten runs of the NS design with $1$ thread ($NS_{B1}$). For
that, we use the following formula for the overhead $O_{DBT} = D_{BT}
/ NS_{B1}$.  After calculating all the overheads $O_{DBT}$ for a
certain design $D$ and number of threads $T$ corresponding to the
several benchmarks $B$, we calculate the respective minimum, average,
maximum and standard deviation overhead ratios.

@@

By observing Table~\ref{tab_batched_overhead}, we can see that, for 1
thread, on the average overhead ratio, local scheduling is sightly
better than batched on the two designs. For the NS design we have
$0.78$ and $0.82$ and for the FS design we have $1.30$ and $1.46$
average overhead ratios, for the local and batched scheduling
strategies, respectively.

%%  As we scale the number of threads, one can observe that,
%% for the NS design both scheduling strategies have similar minimum,
%% average and maximum overhead ratios. For the FS design, the best
%% minimum overhead ratio on $1$, $8$, $16$, $24$ and $32$ threads is
%% always the batched scheduling. For the average and maximum overhead
%% ratio, local scheduling is always better than batched
%% scheduling. However, for the average ratio, the results between both
%% strategies is quite close. We consider this to be quite significant,
%% once the FS design with batched scheduling requires the support of the
%% PAC procedure. For the maximum overhead ratio, the difference between
%% both strategies is higher than for the average overhead ratio, however
%% we hope to reduce the difference with further improvements in the PAC
%% procedure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Further Work}
We have presented a simple and novel approach for combining the FS
design with batched scheduling. Experimental results showed that one
average, the extra structures required for the combination do not seem
to have a big impact in the performance. Further work will include
experimentation in more applications and improvements in the PAC
procedure.
